### 2017-04-17 paper/evaluation.tex
grammar fix

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \SubjectsGithubNotTestable{} projects were untestable
(because of missing dependencies or incompatible testing environment,
for example), and \SubjectsGithubFlaky{} projects were ``flaky''.
\Jbc{Check if this is ok $\rightarrow$} We executed each project's
test suite for three times to identify projects containing flaky tests
and to ignore these tests (\ie, using the \CodeIn{@Ignore} annotation
from JUnit) to avoid introducing noise in our experiments.  Our final
set of subjects consists of \numSubjs{} projects.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular
    projects hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotTestable{} untestable projects\Comment{, and
    \SubjectsGithubFlaky{} projects with flaky tests}. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}

>>>>

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \SubjectsGithubNotTestable{} projects were untestable
(because of missing dependencies or incompatible testing environment,
for example), and \SubjectsGithubFlaky{} projects were ``flaky''.
\Jbc{Check if this is ok $\rightarrow$} We executed each project's
test suite for three times to identify projects containing flaky tests
and ignored these tests (\ie, using the \CodeIn{@Ignore} annotation
from JUnit) to avoid introducing noise in our experiments.  Our final
set of subjects consists of \numSubjs{} projects.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular
    projects hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support and
    \SubjectsGithubNotTestable{} untestable projects\Comment{, and
    \SubjectsGithubFlaky{} projects with flaky tests}. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}
